---
title: "HW4_Q1"
author: "Daniil Deych, Reilly Blakeslee, Alex Mykietyn"
date: "`r Sys.Date()`"
output: pdf_document:
          keep_md: TRUE
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(tibble)
library(ggplot2)
library(igraph)
library(dplyr)
library(readr)
library(Hmisc)
library(arules)
library(arulesViz)
library(knitr)
library(igraph)
library(RColorBrewer)
```

# Question 1

## PCA

The two graphs below represent the PCA analysis of the wine data. The PCA algorithm had little trouble distinguishing between the two "colors" of the wines, as can be easily seen from the first graph.

However, the PCA had difficulties with determining quality of the wine, as determinied by the wine snobs. On further thought that conclusion should not be surprising, since wine quality is extremely subjective, and if there existed such deterministic formula that creates high quality wine, it would very easily replicated. Such is not the case.

```{r, echo=FALSE}
library(tidyverse)
library(tibble)
library(ggplot2)
library(dplyr)

wine_data = read.csv("data/wine.csv")

wine_data_ID = tibble::rowid_to_column(wine_data, "id")

wine_data_colorless <-  select(wine_data_ID, -color, -quality)

PCA_wine_color = prcomp(wine_data_colorless, scale. = TRUE, rank = 2)
loadings_wine_color = PCA_wine_color$rotation
scores_wine_color = PCA_wine_color$x

qplot(scores_wine_color[,1], scores_wine_color[,2], color=wine_data_ID$color, xlab='Component 1', ylab='Count')

PCA_wine_quality= prcomp(wine_data_colorless, scale. = TRUE, rank = 2)
loadings_wine_quality = PCA_wine_quality$rotation
scores_wine_quality = PCA_wine_quality$x

qplot(scores_wine_quality[,1], scores_wine_quality[,2], color=wine_data_ID$quality, xlab='Component 1', ylab='Component 2')

```

## Clustering Analysis

Clustering analysis did not provide any useful results. Below is a plot of the K-means algorithm, with k=2 andk=7, in hopes that it would be able to break down the data either by color (red or white) or quality (3-9). However, as the graphs below suggeset no appropriate clustering took place, which after doing some research isn't surprising, as none of the chemical properties of the data aren't actually indicative of grape color on their own. As for quality, similarily to the PCA analysis, it appears that chemical composition (that is provided by the data) isn't deterministic of the determined quality.

Note. I ended up choosing pH and sulphates as my variables after some trial and error playing with other variables. No other combination provided any significant visual distinctions in the types of wine.

```{r, echo=FAlSE}

library(foreach)
library(mosaic)

wine_data_colorless2 <- select(wine_data, -color, -quality)

wine_data_colorless2_scaled = scale(wine_data_colorless2, center = TRUE, scale = TRUE)

wine_cluster1 = kmeans(wine_data_colorless2_scaled, 7, n=25)

wine_cluster2 = kmeans(wine_data_colorless2_scaled, 2, n=25)

qplot(pH, sulphates,  data=wine_data, color=factor(wine_cluster1$cluster))

qplot(pH, sulphates, data=wine_data, color=factor(wine_cluster2$cluster))
```

# Question 2

Here we attempt to find market segments for the company by finding correlations between the topic of user's twitter posts. We construct a graph showing an edge between two topics if the topics have correlation greater than 0.25:

```{r, include = FALSE}
social_marketing <- read.csv("data/social_marketing.csv")
df = social_marketing

X = df[,-1]

CM2 <- rcorr(as.matrix(X))
CM2

flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
  )
}

# corrplot(CM2$r, type="upper", order="hclust", 
#          p.mat = CM2$P, sig.level = 0.01, insig = "blank")

CM4 <- flattenCorrMatrix(CM2$r, CM2$P)

```

```{r, include = FALSE}
#Graph 4 Correlation >0.25
CM7 = CM4 %>% filter(cor >0.25)
CM7 <- CM7[,1:2]
set.seed(19)
g3 <- graph.data.frame(CM7, directed=FALSE)
V(g3)$label.cex <- seq(0.15,1,length.out=1)
plot(g3, vertex.label = V(g3)$name, vertex.size = 15,
     edge.arrow.size = 0.5)

```

```{r, echo=FALSE}
plot(g3, vertex.label = V(g3)$name, vertex.size = 15,
     edge.arrow.size = 0.5)
```

We can distinctly see 7 different groups of correlated user interests.

Group 1 - Adults with kids (School, Food, Family, Parenting, Religion, Sports Fandom)

Given the topics of school, parenting and family it is reasonable to assume that this segment is comprised of people who either have children or want children. Family friendly messaging is likely likely important for this segment. The sports fandom interest also suggests it may be disproportionately male.

Group 2 - Current Events (Politics, Travel, Computers, News, Automotive)

Politics is the center of this network and is correlated with all other members. This market segment also seems to keep up with world trends in culture and technology following the news, travel and computers. Corporate messaging that is current and relevant would be best for this group.

Group 3 - Aesthetically Oriented (Beauty, Fashion, Cooking, Photo Sharing, Shopping, Chatter)

This market segment is likely highly keen on the image with interests in beauty, shopping, photo sharing and fashion. There is also a chance this segment is disproportionately female.

Group 4 - Creatives (Art, TV_fim, Music)

Here we have individuals who might appreciate uniqe and original marketing with an artistic bent.

Group 5 - College Men (Sports_playing, online_gaming, college_uni)

This segment seems to be largely comprised of young men, historically advertisement using attractive women has been targeted for this group.

Group 6 - Health (health_nutrition, personal_fitness, outdoors)

This group is very active and concerned with personal health, any health features of the drink should be highlighted for this group.

Group 7 - Bots (Spam, Adult)

These are likely not real followers.

# Question 3

For this rule selection, I set the minimum support to 0.003, minimum confidence to 0.2, and minimum length of the rules to 2. These thresholds were chosen based on trial and error to find a good balance between the number of rules generated and their interestingness. Some of the interesting associations that we see are people who buy instant food products are more likely to buy hamburger meat, people who buy flour are more likely to buy sugar, and people who buy processed cheese are more likely to buy white bread. These rules all make sense - baking, sandwich making, easy meals, etc. The relative frequency plots as well as association plots and top 5 association rules are shown below.

```{r, include = FALSE}
groceries <- read.transactions("data/groceries.txt", sep = ",")
summary(groceries)
inspect(groceries[1:5])
```

```{r, include = FALSE}
rules <- apriori(groceries, parameter = list(support = 0.003, confidence = 0.2, minlen = 2))

t1 = inspect(sort(rules[1:5], by = "lift"))
```

```{r, echo = FALSE, warning=FALSE}

kable(t1)
plot(rules, jitter = 0)
arules::itemFrequencyPlot(groceries, topN = 20,
                          col = brewer.pal(8, 'Pastel2'),
                          main = 'Relative Item Frequency Plot',
                          type = "relative",
                          ylab = "Item Frequency (Relative)")
groceries_graph = associations2igraph(subset(rules, lift>2), associationsAsNodes = FALSE)


```
